### 2023-10-31 design/models.tex
Wrong links

This is taken care of using in reality two parts, the actual voltage multiplier (\cref{eq:voltMult}) and a non inverting amplifier (\cref{eq:invAmp}), the circuit of which is available in \cref{apsec:invAmp}.

@@

Where $V_{out}$ is the output voltage the inverting amplifier (\cref{apsec:invAmp}), $V_{voltMult}$ is the out voltage of the voltage multiplier itself and $V_{in_1}$ and $V_{in_2}$ are the input voltages.

>>>>

This is taken care of using in reality two parts, the actual voltage multiplier (\cref{eq:voltMult}) and a non inverting amplifier (\cref{eq:invAmp}), the circuit of which is available in \cref{apsec:sumInv}.

@@

Where $V_{out}$ is the output voltage the inverting amplifier (\cref{apsec:sumInv}), $V_{voltMult}$ is the out voltage of the voltage multiplier itself and $V_{in_1}$ and $V_{in_2}$ are the input voltages.
